\chapter{Introduction}

Augmented reality (AR) technologies have revolutionized various industries, offering innovative solutions to complex problems. Quality control systems are one such area where AR can provide immense value. While similar applications exist on platforms like the iPad, their limitations in spatial capabilities and less intuitive interaction methods make them less suitable for high-precision tasks. In this project, we have developed a quality control system tailored for the Apple Vision Pro (AVP), leveraging its advanced spatial capabilities, immersive experience, and intuitive gesture-based controls.

Our solution addresses the limitations of traditional systems by integrating advanced features such as 3D CAD model alignment, real-time object tracking, and automated reporting. These enhancements make the AVP-based quality control system ideal for industries demanding high precision and efficiency.

\section{Project Definition}

The aim of this project is to develop a quality control system specifically designed for the Apple Vision Pro (AVP). Unlike iPads, which have limited spatial features, the AVP offers advanced spatial capabilities and immersive interaction methods that make it ideal for high-precision tasks. This system leverages the AVP’s strengths to improve accuracy and efficiency in quality control processes.

The key functionalities include aligning 3D CAD models with real-world objects, enabling interactive inspections at predefined points, and generating detailed quality analysis reports. By addressing the limitations of tablet-based systems, this project aims to provide an innovative solution for industries requiring precise quality control.


% This project focuses on designing and implementing a quality control system for the Apple Vision Pro (AVP). The system utilizes the AVP's cutting-edge spatial and interaction capabilities to enhance accuracy and user experience. The core functionality revolves around:
% \begin{itemize}
%     \item Aligning 3D CAD models with real-world objects to identify differences.
%     \item Providing users with tools for interactive and natural inspection using gesture-based controls.
%     \item Generating quality analysis reports in Excel format for documentation and review.
%     \item Allowing users to inspect predefined points on models for detailed quality control.
% \end{itemize}

% During the inspection process, users can select specific inspection points on the model to perform quality checks. These inspections can include:
% \begin{itemize}
%     \item Yes/No Verification: Confirming whether a feature meets the required specifications.
%     \item Description-based Analysis: Providing detailed notes about the inspected feature.
%     \item Count-based Evaluation: Counting the number of specific elements.
% \end{itemize}

% The application is designed to support industries where precise quality control is critical, such as manufacturing, automotive, and aerospace.

\section{Project Aims}

The primary aims of this project are as follows:
\begin{enumerate}
    \item \textbf{Enhanced User Experience:} Develop an intuitive UI/UX interface with gesture-based controls, including eye-tracking and finger interactions.
    \item \textbf{Precise Model Alignment:} Implement a robust algorithm for aligning 3D CAD models with real-world objects, ensuring high accuracy.
    \item \textbf{Inspection Points:} Enable users to select and inspect specific points on models, offering flexible options like yes/no, descriptions, and counts for quality control.
    \item \textbf{Automated Reporting:} Create a reporting feature that allows users to extract detailed quality analysis in Excel format.
    \item \textbf{Performance Optimization:} Ensure the system operates efficiently, achieving high frame rates, low latency, and inspection speeds comparable to or better than tablet-based solutions.
\end{enumerate}

These aims are designed to address the current limitations of traditional quality control systems and utilize the advanced capabilities of the Apple Vision Pro to deliver an innovative and efficient solution.
